Inference methods comparison for the simplified Naomi model

### 2023-02-04 src/naomi-simple_compare/comparison.Rmd
Save the beta_rho results to import back into my Laplace development pipeline
Add adam method to comparison #20

```{r}
tmb <- readRDS("depends/tmb.rds")
aghq <- readRDS("depends/aghq.rds")
tmbstan <- readRDS("depends/tmbstan.rds")
```

@@

```{r}
data.frame(
  "TMB" = tmb$time,
  "aghq" = aghq$time,
  "tmbstan" = tmbstan$time
)
```

@@

```{r}
histogram_plot("beta_rho", i = 1)
histogram_plot("beta_anc_rho")
```

@@

```{r}
ks_helper <- function(par) to_ks_df(par) %>% ks_plot(par = par)

@@

ks_helper("u_rho_x")
ks_helper("u_rho_xs")
ks_helper("us_rho_x")
ks_helper("us_rho_xs")
ks_helper("u_rho_a")
ks_helper("u_rho_as")

ks_helper("u_alpha_x")
ks_helper("u_alpha_xs")
ks_helper("us_alpha_x")
ks_helper("us_alpha_xs")
ks_helper("u_alpha_a")
ks_helper("u_alpha_as")
ks_helper("u_alpha_xa")

ks_helper("ui_anc_rho_x")
ks_helper("ui_anc_alpha_x")
ks_helper("log_or_gamma")
```

>>>>

```{r}
tmb <- readRDS("depends/tmb.rds")
aghq <- readRDS("depends/aghq.rds")
adam <- readRDS("depends/adam.rds")
tmbstan <- readRDS("depends/tmbstan.rds")
```

@@

```{r}
data.frame(
  "TMB" = tmb$time,
  "aghq" = aghq$time,
  "adam" = adam$time,
  "tmbstan" = tmbstan$time
)

adam <- adam$adam
```

@@

```{r}
beta_rho <- histogram_plot("beta_rho", i = 1, return_df = TRUE)
beta_rho$plot
saveRDS(beta_rho$df, "beta_rho.rds")

histogram_plot("beta_anc_rho")
```

@@

```{r}
ks_helper <- function(par, ...) {
  to_ks_df(par) %>% ks_plot(par, ...)
}

@@

ks_helper("u_rho_x")
ks_helper("u_rho_x", method1 = "TMB", method2 = "adam")

ks_helper("u_rho_xs")
ks_helper("u_rho_xs", method1 = "TMB", method2 = "adam")

ks_helper("us_rho_x")
ks_helper("us_rho_x", method1 = "TMB", method2 = "adam")

ks_helper("us_rho_xs")
ks_helper("us_rho_xs", method1 = "TMB", method2 = "adam")

ks_helper("u_rho_a")
ks_helper("u_rho_a", method1 = "TMB", method2 = "adam")

ks_helper("u_rho_as")
ks_helper("u_rho_as", method1 = "TMB", method2 = "adam")

ks_helper("u_alpha_x")
ks_helper("u_alpha_x", method1 = "TMB", method2 = "adam")

ks_helper("u_alpha_xs")
ks_helper("u_alpha_xs", method1 = "TMB", method2 = "adam")

ks_helper("us_alpha_x")
ks_helper("us_alpha_x", method1 = "TMB", method2 = "adam")

ks_helper("us_alpha_xs")
ks_helper("us_alpha_xs", method1 = "TMB", method2 = "adam")

ks_helper("u_alpha_a")
ks_helper("u_alpha_a", method1 = "TMB", method2 = "adam")

ks_helper("u_alpha_as")
ks_helper("u_alpha_as", method1 = "TMB", method2 = "adam")

ks_helper("u_alpha_xa")
ks_helper("u_alpha_xa", method1 = "TMB", method2 = "adam")

ks_helper("ui_anc_rho_x")
ks_helper("ui_anc_rho_x", method1 = "TMB", method2 = "adam")

ks_helper("ui_anc_alpha_x")
ks_helper("ui_anc_alpha_x", method1 = "TMB", method2 = "adam")

ks_helper("log_or_gamma")
ks_helper("log_or_gamma", method1 = "TMB", method2 = "adam")
```
